\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Chandrahas Nalabotu} \\ \vspace{5pt}
    \small \faEnvelope \hspace{2pt} \href{mailto:101chandrahas@gmail.com}{\underline{101chandrahas@gmail.com}} $|$ 
    \faLink \hspace{2pt} \href{https://101cn.github.io/portfolioCN-/}{\underline{101cn.github.io/portfolioCN-/}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Leicester}{2024 -- Present}
      {Mechanical Engineering MEng}{}
      \resumeItemListStart
        \resumeItem{Year 1 and 2 - 1st}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience / Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Aerolabs CFD Analyst / Avionics Engineer -- UAS Challenge}{September 2025 -- Present}
      {CFD and Electronic Framework}{}
      \resumeItemListStart
        \resumeItem{Ran 3D CFD simulations in STAR-CCM+ on a drone airframe, increasing lift coefficient from 1.0 to 1.6 by adding secondary flaps, enabling lower minimum flight speed.}
        \resumeItem{Reduced CFD simulation runtime from 6 hours to $\sim$2 hours by tuning solver settings and convergence criteria under senior team member guidance.}
        \resumeItem{Configured flight controller optimising control delivery and sensitivity.}
      \resumeItemListEnd

    \resumeSubheading
      {Innex1 Rover - Lunabotics 2026}{September 2025 -- Present}
      {Software \& Electrical Architecture}{}
      \resumeItemListStart
        \resumeItem{Built a 5-topic ROS2 architecture with dedicated bridges for drivetrain, excavation and actuator subsystems, reducing controller input to rover response latency from 2.5s to 0.6s and enabling controller teleoperation via Pygame.}
        \resumeItem{Reduced live camera feed latency from 30s to $\sim$1s at 40Hz through bandwidth reduction over a ROS2/WebSocket pipeline to mission control.}
        \resumeItem{Designed fail-closed motion safety logic with a 200ms stale-command timeout and stall-detection encoder verification to prevent uncontrolled spinning under low traction.}
        \resumeItem{Separated 60A motor power and 15A compute power domains with independent fusing and a fault-latching E-stop circuit, preserving telemetry and compute uptime during an E-stop event.}
      \resumeItemListEnd

    \resumeSubheading
      {Surgical Instrument Carrier -- Rover Delivery}{September 2025 -- March 2026}
      {Hardware \& Firmware Engineering}{}
      \resumeItemListStart
        \resumeItem{Reduced electronics expenditure by $\sim$30\% by designing three distinct hardware subsystems (drive, indication, and servo) using off-the-shelf Arduino UNOs in EasyEDA rather than manufacturing custom PCBs.}
        \resumeItem{Achieved autonomous line-following capabilities by writing C++ control logic that continuously processed IR and Time-of-Flight sensor data to regulate dual brushed DC drive motors.}
        \resumeItem{Integrated a centralized firmware architecture across 3 separate hardware modules, successfully synchronizing the autonomous drive systems with the servo-actuated payload delivery mechanism.}
      \resumeItemListEnd

    \resumeSubheading
      {Single Axis Stabilizer}{September 2023 -- May 2024}
      {NEA Coursework}{}
      \resumeItemListStart
        \resumeItem{Engineered a single-axis camera mount that actively counteracts external disturbance using IMU feedback while enabling continuous 360$^\circ$ rotation, controlled via Arduino.}
        \resumeItem{Reduced angular tracking error by 30\% and eliminated dropped interrupts by refactoring open-source stabilization control code.}
        \resumeItem{Designed mechanical housing and PCB layout using Fusion 360 and EasyEDA, standardizing hole and via sizing to meet manufacturing tolerances.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Software}{: Solidworks, Fusion 360, Excel, STAR CCM+} \\
     \textbf{Coding / Frameworks}{: Python, Arduino, C++, MATLAB, Simulink, ROS2, Linux distributions} \\
     \textbf{Manufacturing}{: 3D prints, lathe, laser cutter, soldering, standard workshop machining equipment}
    }}
 \end{itemize}

\end{document}
